Dac summary 01/19/2021

### 2021-04-16 final_dac_summary_pull_20210119.Rmd
Add files via upload

data_empi_acc_f_phq <- data[which(data$Provider %in% ms_providers),] #n = 17067
table(data_empi_acc_f_phq$Provider)

@@

# number of unique scanners and scans
print(paste0("Number of unique procedure names (ie. MRI Head w/out contrast; MRI Source Images): ",  length(unique(data_empi_acc_f_phq$PROC_CODE)))) #n = 11
print(paste0("Number of unique department names (ie. RAD HUP PCAM Ground): ",  length(unique(data_empi_acc_f_phq$DEPARTMENT_NAME)))) #n = 3
print(paste0("Number of unique modalities (ie. HUP PCAM GR MR4 3T; MR6 3T): ",  length(unique(data_empi_acc_f_phq$MODALITY)))) #n = 11
print(paste0("Number of unique accession #s n= ", length(unique(data_empi_acc_f_phq$ACCESSION_NUM)))) # n = 17067

#### PHQ-2 and PHQ-9 summaries
#phq-2;
print(paste0("N PHQ-2 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.2)))) #n = 4701

#phq-9
print(paste0("N PHQ-9 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.9)))) #n = 274

@@

#### ICD 9/10 for Depression
dep_df <- data_empi_acc_f_phq[grep("F3", data_empi_acc_f_phq$ICD10),] #n = 2339
num_depression <- dim(dep_df)[1]
unique_empi <- which(unique(data_empi_acc_f_phq$EMPI) %in% data_empi_acc_f_phq$EMPI) #index of the locations of unique empis; n = 3885
num_unique_EMPI_and_dep <- length(unique(dep_df$EMPI)) #n = 633

@@

##### PHQ2 or 9 + ICD 9/10 Depression
num_phq2_and_dep <- length(which(!is.na(dep_df$PHQ.2))) #n = 1049
print(paste0("N with ICD 9/10 codes for depression and phq2 (ALL SCANS) = ", num_phq2_and_dep, " out of ", dim(dep_df)[1]))

num_phq9_and_dep <- length(which(!is.na(dep_df$PHQ.9))) #n=153
print(paste0("N with ICD 9/10 codes for depression and phq9 (ALL SCANS) = ", num_phq9_and_dep, " out of ", dim(dep_df)[1]))

#### # unique people with dep dx and phq2/9 -> working on this
dep_dx_phq2_unique <- length(unique(dep_df$EMPI[!is.na(dep_df$PHQ.2)])) #n = 266
print(paste0("N with ICD 9/10 codes for depression and phq2 (unique) = ", dep_dx_phq2_unique, " out of ", dim(dep_df)[1]))

dep_dx_phq9_unique <- length(unique(dep_df$EMPI[!is.na(dep_df$PHQ.9)])) #n = 51
print(paste0("N with ICD 9/10 codes for depression and phq9 (unique) = ", dep_dx_phq9_unique, " out of ", dim(dep_df)[1]))

>>>>

#keep people with MS providers 
data_empi_acc_f_phq <- data[which(data$Provider %in% ms_providers),] #n = 17067

#keep people with ICD10 code G35 (this is the same # as people with IC9 - 340)
data_empi_acc_f_phq <- data_empi_acc_f_phq[grep("G35", data_empi_acc_f_phq$ICD10),] #n = 16830
table(data_empi_acc_f_phq$Provider)

@@

# number of unique scanners and scans
print(paste0("Number of unique procedure names (ie. MRI Head w/out contrast; MRI Source Images): ",  length(unique(data_empi_acc_f_phq$PROC_CODE)))) #n = 10
print(paste0("Number of unique department names (ie. RAD HUP PCAM Ground): ",  length(unique(data_empi_acc_f_phq$DEPARTMENT_NAME)))) #n = 3
print(paste0("Number of unique modalities (ie. HUP PCAM GR MR4 3T; MR6 3T): ",  length(unique(data_empi_acc_f_phq$MODALITY)))) #n = 11
print(paste0("Number of unique accession #s n= ", length(unique(data_empi_acc_f_phq$ACCESSION_NUM)))) # n = 16830

#### PHQ-2 and PHQ-9 summaries
#phq-2;
print(paste0("N PHQ-2 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.2)))) #n = 4606

#phq-9
print(paste0("N PHQ-9 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.9)))) #n = 261

@@

#### ICD 9/10 for Depression
dep_df <- data_empi_acc_f_phq[grep("F3", data_empi_acc_f_phq$ICD10),] #n = 2123
num_depression <- dim(dep_df)[1]
unique_empi <- which(unique(data_empi_acc_f_phq$EMPI) %in% data_empi_acc_f_phq$EMPI) #index of the locations of unique empis; n = 3885
num_unique_EMPI_and_dep <- length(unique(dep_df$EMPI)) #n = 493

@@

##### PHQ2 or 9 + ICD 9/10 Depression
num_phq2_and_dep <- length(which(!is.na(dep_df$PHQ.2))) #n = 960
print(paste0("N with ICD 9/10 codes for depression and phq2 (ALL SCANS) = ", num_phq2_and_dep, " out of ", dim(dep_df)[1]))

num_phq9_and_dep <- length(which(!is.na(dep_df$PHQ.9))) #n=140
print(paste0("N with ICD 9/10 codes for depression and phq9 (ALL SCANS) = ", num_phq9_and_dep, " out of ", dim(dep_df)[1]))

#### # unique people with dep dx and phq2/9 -> working on this
dep_dx_phq2_unique <- length(unique(dep_df$EMPI[!is.na(dep_df$PHQ.2)])) #n = 201
print(paste0("N with ICD 9/10 codes for depression and phq2 (unique) = ", dep_dx_phq2_unique, " out of ", dim(dep_df)[1]))

dep_dx_phq9_unique <- length(unique(dep_df$EMPI[!is.na(dep_df$PHQ.9)])) #n = 43
print(paste0("N with ICD 9/10 codes for depression and phq9 (unique) = ", dep_dx_phq9_unique, " out of ", dim(dep_df)[1]))
